An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-22 Revision/response.tex

For range filtering, please see section 4.3.1.

\textcolor{blue}{"As for the Search peak memory usage, we can find from the Figure ~\ref{fig:range filtering search peak memory} that it is basically consistent with the Build peak memory usage trend. The algorithm needs to load the complete index into memory during search. Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead. For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend."}

%%%%%%%%%%%%%%%%%%%%%% R8 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run Scalability experiments with larger datasets.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your valuable suggestion regarding our experiments. In Section 4.2.4, we add experiments on the Deep100M dataset. The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset. In particular, StitchedVamana performs poorly on Deep100M. Please see section 4.2.4.

\textcolor{blue}{"On the 100M dataset, UNG and NHQ still exhibit excellent performance, demonstrating their good adaptability to large-scale datasets; however, this also comes with significant memory overhead. The clustering-based algorithm \texttt{Faiss+HQI\_Batch} shows moderate performance but has very low memory overhead, which makes it highly attractive for practical applications. We did not present the experimental results for StitchedVamana because we found that its recall consistently remained at a very low level. Its search starting point is set to 0 by default, and when the entry point is far from the target area, it easily gets stuck in a local optimum, making it difficult to navigate to the vicinity of the correct point."}

@@

We conducted experiments on both datasets and present the performance analysis for various algorithms in \textcolor{blue}{Sections 4.2.2 and 4.3.2}. Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.

Regarding the more intricate semantic relationships—such as those between vectors and attributes, or among different attributes themselves—current hybrid search algorithms do not explicitly model or leverage such correlations. Nevertheless, our evaluation covers a range of realistic scenarios, including multi-attribute settings and diverse  distributions, to assess the generalization ability of the algorithms.

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Some figures (e.g., performance under different attribute distributions or selectivity) are dense and could benefit from cleaner presentation or summarization to improve readability.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your feedback. We improve the readability of the two figures in Section 4.2.3, and please see Meta-Review R1 for details.

### 2025-07-22 VLDB2026/main.tex
change

	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while \underline{the database's peak memory usage} is comparatively lower.}

@@

		%\vspace{0.1cm}
		\begin{subfigure}[t]{0.332\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel.pdf}
			\caption{\footnotesize MultiModel}
			\label{fig:MultiModel}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.315\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_85.pdf}
			\caption{\footnotesize Different Computer}
			\label{fig:Different Computer}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.315\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_100M.pdf}
			\caption{\footnotesize Big Dataset}
			\label{fig:Big Dataset}
		\end{subfigure}

@@

		%\vspace{0.1cm}
		\begin{subfigure}[t]{0.332\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/exp/range_multimodel.pdf}
			\caption{\footnotesize MultiModel}
			\label{fig:MultiModel range}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.315\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
			\caption{\footnotesize Different Computer}
			\label{fig:Different Computer range}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.315\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
			\caption{\footnotesize Big Dataset}
			\label{fig:Big Dataset range}
		\end{subfigure}

>>>>

	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while \underline{the peak memory usage of database} is comparatively lower.}

@@

		%\vspace{0.1cm}
		\begin{subfigure}[t]{0.507\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel.pdf}
			\caption{\footnotesize MultiModel}
			\label{fig:MultiModel}
		\end{subfigure}	
		\hfill
		\begin{subfigure}[t]{0.48\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel_1.pdf}
			\caption{\footnotesize MultiModel}
			\label{fig:MultiModel}
		\end{subfigure}

		\begin{subfigure}[t]{0.507\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_85.pdf}
			\caption{\footnotesize Different Computer}
			\label{fig:Different Computer}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.48\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_100M.pdf}
			\caption{\footnotesize Big Dataset}
			\label{fig:Big Dataset}
		\end{subfigure}

@@

		%\vspace{0.1cm}
		\begin{subfigure}[t]{0.507\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/exp/range_multimodel.pdf}
			\caption{\footnotesize MultiModel}
			\label{fig:MultiModel range}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.48\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/exp/range_multimodel_1.pdf}
			\caption{\footnotesize MultiModel}
			\label{fig:MultiModel range}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.507\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
			\caption{\footnotesize Different Computer}
			\label{fig:Different Computer range}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.48\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
			\caption{\footnotesize Big Dataset}
			\label{fig:Big Dataset range}
		\end{subfigure}
